An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-21 paper.tex
Minor cleanup of citations
Remove windows crap

\documentclass[11pt, conference, , compsocconf]{IEEEtran}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usepackage[colorlinks,urlcolor=blue,citecolor=hotpink,linkcolor=blue]{hyperref}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,249,234}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102} 
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

@@

We can analyze the spread of information between $A$, $B$, and $C$
as a process on a graph that changes over time.  
Such graphs are known as evolving graphs.
% Evolving graphs are models to study this kind of scenario where the 
% interrelations between entities are time-dependent.
% We assume that the reader is familiar with the basic graph terminology. 
% All the necessary material can be found in}.
We follow the notation of (static) graphs in  \cite{even12} and \cite{kegi11}.
In general, a evolving graph $G(t) = (V(t), E(t))$ is  a graph where the node set
and edge set are functions of time $t$.
However, in different literatures the term ``evolving graph'' has been
used to refer to slightly different models. 
 Flajolet et al. \cite{fkp89} use the term to mean the evolution of random graphs.
Bahmani et al. \cite{bkmu12} use the term to mean a sequence of graphs where
the difference between two consecutive graphs is small.
Similar models are also investigated using the term ``evolving network'' and 
``time-dependent graph''.

@@

% Given a graph and a source node $s$, 
% the breadth-first search (BFS) systematically discover every node that is reachable from $s$. 
% As the name suggested, BFS expands the frontier of discovered regions
% uniformly across the breadth, i.e., the algorithm discovers all nodes
% that are $k$ walks away from $s$ before discovering any nodes that are
% $k+1$ walks away. 
A temporal path is the basic element to 
 define almost  all important evolving graph algorithms.
Matrix-matrix multiplication between consecutive adjacency matrices
were commonly used as a means of determining temporal paths \cite{gphe11} \cite{grihig13}. However, we show
in one specific case it fails to include all the temporal paths and thus should not be used 
for searching evolving graphs in general.

Breadth-first search is probably the most basic graph searching algorithm and 
it is also the building block of other graph algorithms like minimum spanning tree 
and shortest path \cite{ckrs09}.
Despite the fact that graph metrics \cite{ntmm13} \cite{tmml09} \cite{tsmm09} and 
various centrality measures (including Katz  \cite{gphe11} \cite{grihig13}, 
betweenness \cite{alhi15}, and closeness  \cite{tmml10}) 
have been generalized for evolving graphs,
a BFS for evolving graphs, which we shall call it \emph{evolving-graph BFS},
was never explicitly described or verified.

>>>>

\documentclass[11pt,conference,compsocconf]{IEEEtran}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usepackage[colorlinks,urlcolor=blue,citecolor=hotpink,linkcolor=blue]{hyperref}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,249,234}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

@@

We can analyze the spread of information between $A$, $B$, and $C$
as a process on a graph that changes over time.
Such graphs are known as evolving graphs.
% Evolving graphs are models to study this kind of scenario where the
% interrelations between entities are time-dependent.
% We assume that the reader is familiar with the basic graph terminology.
% All the necessary material can be found in}.
We follow the notation of (static) graphs in \cite{even12,kegi11}.
In general, a evolving graph $G(t) = (V(t), E(t))$ is  a graph where the node set
and edge set are functions of time $t$.
However, in different literatures the term ``evolving graph'' has been
used to refer to slightly different models.
 Flajolet et al. \cite{fkp89} use the term to mean the evolution of random graphs.
Bahmani et al. \cite{bkmu12} use the term to mean a sequence of graphs where
the difference between two consecutive graphs is small.
Similar models are also investigated using the term ``evolving network'' and
``time-dependent graph''.

@@

% Given a graph and a source node $s$,
% the breadth-first search (BFS) systematically discover every node that is reachable from $s$.
% As the name suggested, BFS expands the frontier of discovered regions
% uniformly across the breadth, i.e., the algorithm discovers all nodes
% that are $k$ walks away from $s$ before discovering any nodes that are
% $k+1$ walks away.
A temporal path is the basic element to
 define almost  all important evolving graph algorithms.
Matrix-matrix multiplication between consecutive adjacency matrices
were commonly used as a means of determining temporal paths \cite{gphe11,grihig13}. However, we show
in one specific case it fails to include all the temporal paths and thus should not be used
for searching evolving graphs in general.

Breadth-first search is probably the most basic graph searching algorithm and
it is also the building block of other graph algorithms like minimum spanning tree
and shortest path \cite{ckrs09}.
Despite the fact that graph metrics \cite{ntmm13,tmml09,tsmm09} and
various centrality measures like Katz centrality~\cite{gphe11,grihig13},
betweenness \cite{alhi15}, and closeness \cite{tmml10})
have been generalized for evolving graphs,
a BFS for evolving graphs, which we shall call it \emph{evolving-graph BFS},
was never explicitly described or verified.
